---
title: "Download random HD images from various unsplash.com categories in R using the Quickcode package"
author: "Obi Obianom and Brice Richard"
date: "2023-10-22"
output: html_document
---

```{r}
# install quickcode if not available
# install.packages(quickcode)

# load quickcode library
library(quickcode)
clean() #clear the environment

# let's load the r2resize to provide toolbars for the image resizing
library(r2resize)
add.resizer(line.color = "red", thumb.height = "3px", line.height = "10px", default.image.width = "30%")

```

## Download 3 random images from the school category and display

For this example, we will download 3 random png images from the web in the category of 'school' to a temp directory and then display it. The r2resize package provides the image resizer that lets us view the images nicely below.

```{r download school images}
storlocation <- tempdir()
genRandImg(fp = storlocation, n = 3, cat = "school", ext = "png")

getdownloadedfiles = list.files(path = storlocation, pattern = ".png", full.names = TRUE)
```

Display the images:

`r paste0("![](",getdownloadedfiles[1],")")`
`r paste0("![](",getdownloadedfiles[2],")")`
`r paste0("![](",getdownloadedfiles[3],")")`



## Download 6 random images from the animals category and display

For this example, we will download 6 random jpg images from the web in the category of 'school' to a temp directory and then display it. 

```{r download animals images}
storlocation2 <- tempdir()
genRandImg(fp = storlocation2, n = 6, cat = "animals", ext = "jpg")

getdownloadedfiles = list.files(path = storlocation2, pattern = ".jpg", full.names = TRUE)

```

Display the images:

`r paste0("![](",getdownloadedfiles[1],")")`
`r paste0("![](",getdownloadedfiles[2],")")`
`r paste0("![](",getdownloadedfiles[3],")")`
`r paste0("![](",getdownloadedfiles[4],")")`
`r paste0("![](",getdownloadedfiles[5],")")`
`r paste0("![](",getdownloadedfiles[6],")")

## Quick links

 - quickcode github: https://github.com/oobianom/quickcode
 - quickcode CRAN: https://cran.r-project.org/web/packages/quickcode/index.html
 - raw Rmd file for this HTML: https://github.com/oobianom/quickcode/blob/main/inst/sample%20codes/downloadImages.Rmd

